Understanding rankings of financial analysts

### 2015-02-14 doc/understanding/understand-ranking.tex
Initial commit

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
%\onehalfspacing
\doublespace
%\geometry{a4paper}
%\usepackage[natbibapa]{apacite}
\usepackage[longnamesfirst]{natbib}

@@

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}

\begin{document}
<<include=FALSE>>=
library(knitr)
opts_chunk$set(concordance=TRUE)
@

<<load.data,echo=F,warning=FALSE,message=FALSE>>=
strategies <- c('true','recent','all-time')
setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
library(reshape2)
library(data.table)
library(ggplot2)
library(stringr)
library(zoo)
library(xtable)
#load('cache/q.data.RData')
#load('cache/final.bl.RData')
#load('cache/market.set.RData')
#load('cache/example.dt.RData')
load('cache/array.all.vvs.RData')
load('cache/broker.vvs.RData')
source('lib/BL-functions.R')

#library(ProjectTemplate)
#load.project()
###ADD NAs for the case of no ranking ( if NA, no raking)
split.rank <- function(r,n){
if(max(r,na.rm=T)==3|max(r,na.rm=T)==4){n=1}else{if(max(r,na.rm=T)==5|max(r,na.rm=T)==6){n=2}else{if(max(r,na.rm=T)==7|max(r,na.rm=T)==8){n=3}}}#else{if(max(r,na.rm=T)==9|max(r,na.rm=T)==10){n=4}}}}        
        t <- head(r,n)
        b <- tail(r,n)
        replace(replace(replace(replace(r,t,'top'),b,'bottom'),setdiff(r,c(t,b)),'middle'),which(is.na(r)),'noRank')
}

summary.stat <- function(dt){
  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,.N,by=year],dt[,.N,by=list(year,Broker)][,.N,by=year][,N],dt[,.N,by=year][,N]),c('Years','Firms','Brokers','Observations')),data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,.N],'Brokers'=dt[,.N,by=Broker][,.N],'Observations'=prettyNum(dt[,.N],big.mark=' '))))
}

summary.mean.stat <- function(dt,value){
  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,descriptive.f(N),by=year][V1==value][,c(1,3),with=F],dt[,.N,by=list(year,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F],dt[,.N,by=list(year,Stock,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F]),c('Years','Firms','Brokers','Observations')),setnames(data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,descriptive.f(N)][V1==value][,2,with=F],'Brokers'=dt[,.N,by=Broker][,descriptive.f(N)][V1==value][,2,with=F],'Observations'=dt[,.N,by=list(Stock,Broker)][,descriptive.f(N)][V1==value][,2,with=F])),c('Years','Firms','Brokers','Observations')))
}

load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
load('~/Dropbox/workspace/Projects/EPS/cache/eps.dt.RData')
# crossby = function(DT, j, by) {
#     j = substitute(j)
#     ans = rbind(
#         DT[,eval(j),by],
#         DT[,list("Total",eval(j)),by=by[1]],
#         cbind("Total",DT[,eval(j),by=by[2]]),
#         list("Total","Total",DT[,eval(j)]),
#         use.names=FALSE
#         # 'use.names' argument added in data.table v1.8.0
#     )
#     setkeyv(ans,by)
#     ans
# }
# crossby(eps.dt,length(Stock),c('Sector'))

eps.stocks <- intersect(eps.dt$Stock,dimnames(array.all.vvs)[[2]])
eps.dt <- na.omit(setkey(eps.dt[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,clean.s:=.N>=3,by=list(q.id,Stock)][(clean.s)][,q.num:=.GRP,by=q.id],Stock)[eps.stocks])
#complete.dt <- rbindlist(lapply(43:85,function(q){ complete.dt[q.id==q]}))
eps.stocks.rank <- intersect(complete.dt$Stock,dimnames(array.all.vvs)[[2]])

complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks.rank][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'fis.q','q.id')

ind.v <- setnames(data.table(reshape2::melt(array.all.vvs[,eps.stocks,])),c('Quarter','Stock','Var','value'))

desc.ind <- acast(setnames(ind.v[,descriptive.f(value,basic=T),by=.(Var)],c('Var','Stat','value')),Var~Stat,value.var = 'value')

stat.eps <- rbind(setnames(eps.dt[order(Sector),c(lapply(.SD,function(i){length(unique(i))}),.N),by=.(Sector),.SDcols=c('Stock','Broker')],4,'Forecast'),setnames(cbind('Total',eps.dt[order(Sector),c(lapply(.SD,function(i){length(unique(i))}),Forecast=.N),.SDcols=c('Stock','Broker')]),1,'Sector'))

###per broker perspectives
# crossby = function(DT, j, by) {
#     j = substitute(j)
#     ans = rbind(
#         DT[,eval(j),by],
#         DT[,list("Total",eval(j)),by=by[1]],
#         cbind("Total",DT[,eval(j),by=by[2]]),
#         list("Total","Total",DT[,eval(j)]),
#         use.names=FALSE
#         # 'use.names' argument added in data.table v1.8.0
#     )
#     setkeyv(ans,by)
#     ans
# }

num.f.dt <- eps.dt[order(Sector),.N,by=.(q.id,Sector,Broker,Stock)]

per.broker <- setnames(cbind(
        rbind(eps.dt[order(Sector),.N,by=.(q.id,Sector,Broker)][,mean(N),by=Sector],list('Total',eps.dt[order(Sector),.N,by=.(q.id,Sector,Broker)][,mean(N)])),
        rbind(num.f.dt[,.N,by=.(q.id,Sector,Broker)][,mean(N),by=.(Sector)],list('Total',num.f.dt[,.N,by=.(q.id,Sector,Broker)][,mean(N)]))[,V1],
        rbind(num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Broker)][,mean(V1),by=Sector],list('Total',num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Broker)][,mean(V1)]))[,V1],
        rbind(num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Broker)][,mean(V1),by=Sector],list('Total',num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Broker)][,mean(V1)]))[,V1]),c('Sector','Forecast','Stocks','Forecast/stock','Follow time,q'))

###per stock
per.stock <- setnames(cbind(
        rbind(eps.dt[order(Sector),.N,by=.(q.id,Sector,Stock)][,mean(N),by=Sector],list('Total',eps.dt[order(Sector),.N,by=.(q.id,Sector,Stock)][,mean(N)])),
        rbind(num.f.dt[,.N,by=.(q.id,Sector,Stock)][,mean(N),by=.(Sector)],list('Total',num.f.dt[,.N,by=.(q.id,Sector,Stock)][,mean(N)]))[,V1],
        rbind(num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Stock)][,mean(V1),by=Sector],list('Total',num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Stock)][,mean(V1)]))[,V1],
        rbind(num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Stock)][,mean(V1),by=Sector],list('Total',num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Stock)][,mean(V1)]))[,V1]),c('Sector','Forecast','Broker','Forecast/broker','Follow time,q'))

#quarters.eps <- data.table(q.id=complete.dt[order(q.id)][,unique(q.id)])
n <- 3
#ranked.eps.dt <- complete.dt[,merge(setkey(quarters.eps,q.id),.SD,all=T,allow.cartesian=T),by=list(Stock,Broker),.SDcols=c('q.id','Stock','Broker','rank')][,NextPeriod:=split.rank(rank,n),by=list(q.id,Stock)][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))],by=list(q.id,Stock)]
#[,NextPeriod:=paste(NextPeriod,'+1',sep='')]

#ranked.eps.dt$CurrentPeriod <- factor(ranked.eps.dt$CurrentPeriod,levels=c('top','middle','bottom','noRank'))
#ranked.eps.dt$NextPeriod <- factor(ranked.eps.dt$NextPeriod,levels=c('top','middle','bottom','noRank'))
#cache('ranked.eps.dt')
load('cache/ranked.eps.dt.RData')
require(descr)
eps.cont.tab <- ranked.eps.dt[,crosstab(CurrentPeriod,NextPeriod,prop.r=T,prop.t=T,prop.c=T,prop.chisq = F,plot=F)]
#brok.full.stat.pt <- acast(setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
#pt.full.period <- setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view)],c('Statistics','value'))

@
\title{Understanding rankings of financial analysts}
%\title{Understanding and predicting rankings of financial analysts}

 \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
 \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
 \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}

\affil[1]{FEP \& CEF.UP, University of Porto}
\affil[2]{INESC TEC}
\affil[4]{FEUP, University of Porto}

@@

\singlespace
\bibliographystyle{newapa}
\bibliography{/Users/aiguzhinov/Dropbox/Documents/Bibliography/rank}
\doublespace

@@

\begin{table}
\caption{Descriptive statistics of independent variable}
\ Descriptive statists of state variables used to describe the state of the analyst.
\begin{center}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
\toprule
 <<desc-ind,echo=F,results='asis'>>=
data.to.display <- c('nbr.val','mean', 'median','std.dev')
results.final <- desc.ind[,data.to.display]

options(xtable.comment = FALSE)
cat("Variable & Observ & Mean & Median & std.dev\\\\\n")
cat('\\midrule \n')
#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(results.final,display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
@
\bottomrule
\end{tabularx}
\end{center}
\label{tab:ind.vvs}
\end{table}

@@

\begin{center}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Sector & \# stocks & \# core brokers & \# forecasts \\ 
\midrule
<<desc-sector,echo=F,results='asis'>>=
print(xtable(stat.eps,display=c('s','d','d','d','d'),align=c('r',rep('c',ncol(stat.eps)))),only.contents=T,include.colnames=FALSE,include.rownames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(stat.eps)-1),command=c('\\midrule \n')))
@
\bottomrule
\end{tabularx}
\label{table:filtered.summary}
\end{center}
\end{table}

\begin{table}
\caption{Averages of forecasts and stocks from broker and stock perspective}
\ The table presents the averages per quarter statistics based on the per Broker (Panel A) and per Stock (Panel B) perspective. Namely, the columns show the average number of forecast per quarter per Broker (per Stock), average number of Stocks (Brokers) per quarter, average number of forecasts per Stock (Broker) per quarter, and average number of quarters  a broker follows a stock (a stock being followed by a broker).
\begin{center}
%\begin{tabular}{rcccc}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
 \toprule
  Panel A: &\multicolumn{4}{c}{Per broker perspective}\\
  \cline{2-5}
 & Forecasts & Stocks & Forecast/stock & follow time, q \\ 
  \midrule
<<per-brok,echo=F,results='asis'>>=
print(xtable(per.broker,display=c('s','d','f','f','f','f'),align=c('r',rep('c',ncol(per.broker)))),only.contents=T,include.colnames=FALSE,include.rownames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(per.broker)-1),command=c('\\midrule \n')))
@
\midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  Panel B: &\multicolumn{4}{c}{Per stock perspective}\\
  \cline{2-5}
 & Forecasts & Brokers & Forecast/broker & follow time, q \\ 
 \midrule
<<per-stock,echo=F,results='asis'>>=
print(xtable(per.stock,display=c('s','d','f','f','f','f'),align=c('r',rep('c',ncol(per.stock)))),only.contents=T,include.colnames=FALSE,include.rownames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(per.stock)-1),command=c('\\midrule \n')))
@
\bottomrule  
\end{tabularx}
\label{table:forecasts-broker}
\end{center}
\end{table}

<<fig-mean-forecast,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Average number of forecast per quarter',fig.lp='mean-f'>>=
ggplot(num.f.dt[,mean(N),by=.(q.id,Sector)],aes(x=as.Date(q.id),y=V1))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Mean forecast')
@

<<fig-num-forecast,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Number of forecasts',fig.lp='num-f'>>=

ggplot(num.f.dt[,.N,by=.(q.id,Sector)],aes(x=as.Date(q.id),y=N))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Forecasts')
@

<<fig-stocks-brok,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Number of stocks per broker per quarter',fig.lp='num-s-b'>>=
ggplot(num.f.dt[,.N,by=.(q.id,Sector,Broker)][,mean(N),by=.(q.id,Sector)],aes(x=as.Date(q.id),y=V1))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Forecasts')
@

<<fig-brok-stocks,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Number of brokers per stock',fig.lp='num-b-s'>>=
ggplot(num.f.dt[,.N,by=.(q.id,Sector,Stock)][,mean(N),by=.(q.id,Sector)],aes(x=as.Date(q.id),y=V1))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Forecasts')
@

\begin{table}
\caption{Descriptive analysts' rankings}
\label{tab:top}
\ Changes in analysts' \emph{top}, \emph{middle}, \emph{bottom} and \emph{noRank} ranking categories when moving from $t-1$ (rows) to $t$ (columns). Each cell informs a percent of total that compose the ranking category at $t$. Panel A depicts the breakdown of rankings  based on the accuracy in target prices. Panel B shows the rankings that are based on the EPS forecasts.
%\centering
%\ra{1.2}
%\small\addtolength{\tabcolsep}{-2pt}
%Average topN-lastN changes in analyst's rank per quarter with N=3, i.e. in how many stocks, on average per quarter per analsyts, an analyst moved from top.prev to  top.current, last.prev->top.current, top.prev->last.cur, and last.prev->last.current
\begin{center}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  <<desc-rank-eps,echo=F,results='asis'>>=
tab.r <- round(rbind(eps.cont.tab[[3]],Total=apply(eps.cont.tab[[3]],2,sum)),3)*100
rownames(tab.r) <- c('$top_{t-1}$','$middle_{t-1}$','$bottom_{t-1}$','$noRank_{t-1}$','Sum')
colnames(tab.r) <- c('$top_{t}$','$middle_{t}$','$bottom_{t}$','$noRank_{t}$')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=T,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{center}
\end{table}

>>>>

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
%\onehalfspacing
\doublespace
%\geometry{a4paper}
\usepackage[natbibapa]{apacite}
%\usepackage{natbib}

@@

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\title{Understanding rankings of financial analysts}
%\title{Understanding and predicting rankings of financial analysts}

 \author[1,2]{ Artur Aiguzhinov (artur.aiguzhinov@inescporto.pt)}
   \author[1]{
   Ana Paula Serra (aserra@fep.up.pt)}
\affil[1]{Department of Economics \& CEF.UP - University of Porto}

\author[2,3]{
   Carlos Soares (csoares@fe.up.pt)}

\affil[2]{INESC TEC -- Institute for Systems and Computer Engineering of Porto }

\affil[3]{Department of Engineering University of Porto}

@@

\singlespace
\bibliographystyle{apacite}
\bibliography{/Users/aiguzhinov/Dropbox/Documents/Bibliography/rank}
\doublespace

@@

\begin{table}
\caption{Descriptive statistics of independent variable}
\ Descriptive statists of state variables used to describe the state of the analyst.
\begin{center}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
\toprule
Variable & Observ & Mean & Median & std.dev\\
\midrule 
 btm & 144 835 & 5.49 & 0.49 & 230.36 \\ 
  size & 156 456 & 19.82 & 19.75 & 2.09 \\ 
  debt.to.eq & 94 611 & Inf & 0.00 &  \\ 
  accruals & 132 327 &  & -0.02 &  \\ 
  s.vol & 169 405 & 41.86 & 0.04 & 15 195.30 \\ 
  sec.ret & 164 538 & 0.01 & 0.03 & 0.12 \\ 
  growth.gnp & 169 405 & 0.01 & 0.01 & 0.01 \\ 
  inf.rate & 169 405 & 0.01 & 0.01 & 0.01 \\ 
  ret.vix & 164 538 & 0.00 & -0.01 & 0.24 \\ 
  t.bill & 169 405 & 0.04 & 0.04 & 0.02 \\

\bottomrule
\end{tabularx}
\end{center}
\label{tab:ind.vvs}
\end{table}

@@

\begin{center}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Sector & \# stocks & \# core brokers & \# forecasts \\ 
\midrule
 Consumer Discretionary & 436 & 225 & 270 278 \\ 
  Consumer Staples & 103 & 120 & 47 406 \\ 
  Energy & 195 & 133 & 188 231 \\ 
  Financials & 484 & 147 & 206 356 \\ 
  Health Care & 378 & 185 & 148 857 \\ 
  IT & 532 & 255 & 363 950 \\ 
  Industrials & 361 & 212 & 142 704 \\ 
  Materials &  47 &  98 & 21 327 \\ 
  Telecom Services &  12 &  47 & 3 447 \\ 
  Utilities &  88 &  65 & 17 843 \\ 
   \midrule 
Total & 2 635 & 360 & 1 410 399 \\

\bottomrule
\end{tabularx}
\label{table:filtered.summary}
\end{center}
\end{table}

\begin{table}
\caption{Averages of forecasts and stocks from broker and stock perspective}
\ The table presents the averages per quarter statistics based on the per Broker (Panel A) and per Stock (Panel B) perspective. Namely, the columns show the average number of forecast per quarter per Broker (per Stock), average number of Stocks (Brokers) per quarter, average number of forecasts per Stock (Broker) per quarter, and average number of quarters  a broker follows a stock (a stock being followed by a broker).
\begin{center}
%\begin{tabular}{rcccc}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
 \toprule
  Panel A: &\multicolumn{4}{c}{Per broker perspective}\\
  \cline{2-5}
 & Forecasts & Stocks & Forecast/stock & follow time, q \\ 
  \midrule
 Consumer Discretionary & 42.64 & 12.39 & 3.14 & 10.77 \\ 
  Consumer Staples & 15.13 & 5.14 & 2.84 & 12.19 \\ 
  Energy & 61.19 & 13.08 & 3.73 & 11.09 \\ 
  Financials & 52.80 & 14.08 & 3.36 & 11.35 \\ 
  Health Care & 30.85 & 9.51 & 3.01 & 9.86 \\ 
  IT & 53.74 & 14.14 & 3.28 & 10.16 \\ 
  Industrials & 27.40 & 8.63 & 3.12 & 10.17 \\ 
  Materials & 10.06 & 3.17 & 3.18 & 11.26 \\ 
  Telecom Services & 4.84 & 1.78 & 2.78 & 10.09 \\ 
  Utilities & 14.37 & 4.79 & 2.82 & 8.90 \\ 
   \midrule 
Total & 37.78 & 10.46 & 3.17 & 10.60 \\

\midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  Panel B: &\multicolumn{4}{c}{Per stock perspective}\\
  \cline{2-5}
 & Forecasts & Brokers & Forecast/broker & follow time, q \\ 
 \midrule
 Consumer Discretionary & 18.06 & 5.25 & 3.43 & 12.15 \\ 
  Consumer Staples & 13.30 & 4.52 & 3.29 & 12.38 \\ 
  Energy & 30.05 & 6.42 & 4.55 & 12.95 \\ 
  Financials & 16.53 & 4.41 & 3.85 & 11.44 \\ 
  Health Care & 14.98 & 4.62 & 3.35 & 10.19 \\ 
  IT & 21.54 & 5.67 & 3.68 & 11.36 \\ 
  Industrials & 12.14 & 3.82 & 3.41 & 11.66 \\ 
  Materials & 11.89 & 3.75 & 3.44 & 12.35 \\ 
  Telecom Services & 11.45 & 4.21 & 2.82 & 9.95 \\ 
  Utilities & 7.79 & 2.60 & 3.05 & 10.39 \\ 
   \midrule 
Total & 17.57 & 4.86 & 3.60 & 11.51 \\

\bottomrule  
\end{tabularx}
\label{table:forecasts-broker}
\end{center}
\end{table}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/fig-mean-forecast-1} \caption[Average number of forecast per quarter]{Average number of forecast per quarter\label{mean-ffig-mean-forecast}}
\end{figure}

\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/fig-num-forecast-1} \caption[Number of forecasts]{Number of forecasts\label{num-ffig-num-forecast}}
\end{figure}

\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/fig-stocks-brok-1} \caption[Number of stocks per broker per quarter]{Number of stocks per broker per quarter\label{num-s-bfig-stocks-brok}}
\end{figure}

\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/fig-brok-stocks-1} \caption[Number of brokers per stock]{Number of brokers per stock\label{num-b-sfig-brok-stocks}}
\end{figure}

\end{knitrout}

\begin{table}
\caption{Descriptive analysts' rankings}
\label{tab:top}
\ Changes in analysts' \emph{top}, \emph{middle}, \emph{bottom} and \emph{noRank} ranking categories when moving from $t-1$ (rows) to $t$ (columns). Each cell informs a percent of total that compose the ranking category at $t$. Panel A depicts the breakdown of rankings  based on the accuracy in target prices. Panel B shows the rankings that are based on the EPS forecasts.
%\centering
%\ra{1.2}
%\small\addtolength{\tabcolsep}{-2pt}
%Average topN-lastN changes in analyst's rank per quarter with N=3, i.e. in how many stocks, on average per quarter per analsyts, an analyst moved from top.prev to  top.current, last.prev->top.current, top.prev->last.cur, and last.prev->last.current
\begin{center}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
 & $top_{t}$ & $middle_{t}$ & $bottom_{t}$ & $noRank_{t}$ \\ 
 $top_{t-1}$ & 11.6 & 15.2 & 19.4 & 1.2 \\ 
  $middle_{t-1}$ & 45.1 & 32.5 & 27.9 & 3.4 \\ 
  $bottom_{t-1}$ & 13.7 & 7.5 & 11.7 & 0.9 \\ 
  $noRank_{t-1}$ & 29.6 & 44.8 & 41.1 & 94.6 \\ 
  Sum & 100.0 & 100.0 & 100.0 & 100.0 \\

\bottomrule
\end{tabularx}
\end{center}
\end{table}
